Supplements for ``Tensor denoising and completion based on ordinal observations''

### 2020-06-15 old_draft/old_preprint/old_arXiv/ordinalT_supp_v4.tex
organize

\subsection{Clustering results on HCP}
We perform clustering analysis to the 68 brain nodes using the the produce described in Section~\ref{sec:clustering}. Recall that our ordinal tensor method outputs the estimated parameter tensor $\hat\Theta\in\mathbb{R}^{68\times 68\times136}$ with rank $(23,23,8)$.
The number of clusters in the $K$-means is chosen based on the elbow method (see figure~\ref{figure:elbow}). Table~\ref{table:clustering} shows the eight clusters of brain nodes.
\begin{figure}[H]
  \label{figure:elbow}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{elbowm.pdf}
  \end{center}
  \caption{The elbow plot for the number of clusters}
\end{figure}

>>>>

We perform clustering analysis on the 68 brain nodes using the produce described above. Oordinal tensor method outputs the estimated parameter tensor $\hat\Theta\in\mathbb{R}^{68\times 68\times136}$ with rank $(23,23,8)$. We apply $K$-means to the mode-1 principal component matrix of size $68\times 184$ ($184=23\times8$). The elbow method suggests eight clusters among the 68 nodes (see Figure~\ref{figure:elbow}). 
\begin{figure}[H]
  \label{figure:elbow}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{elbowm.pdf}
  \end{center}
  \caption{The elbow plot for the number of clusters}
\end{figure}
